(Re)building cooperation: Effects of a cognitive intervention on cooperative behavior in games

### 2024-02-15 article.Rmd
loaded data only to check equal participants between conditions

d_finished <- readRDS("data/d_finished.csv")
exposure_intervention <- paste0(as.character(d_finished %>% dplyr::select(treatment.intervention) %>% unique()) , as.character(d_finished %>% dplyr::filter(gameNumber == "11", isLastRound) %>% dplyr::select(game_opponent) %>% unique()))

d_finished <- d_finished  %>% mutate(gameNum.f = factor(gameNumber,labels = c("pre", "expo1", "expo2", "expo3","post"),levels=c("1", "11", "12", "13", "2")), 
                              condition  = exposure_intervention) %>% 
                        rename(# Before Exposure
                            rating_cooperative_1 = `ratePLayer_trustGame_1.How cooperative do you think the other player is?`,
                            rating_forgiving_1 = `ratePLayer_trustGame_1.How forgiving do you think the other player is?`,
                            rating_playAgain_1 = `ratePLayer_trustGame_1.If given the choice, would you like to play again with the other player?`,

@@

                            )

@@

# ggplot(mu,aes(x=gameNumber)) + 
#   geom_bar(aes(y=mean_forgiv, stat = "identity", position = "dodge", color="blue")) + 
#   geom_bar(aes(y=mean_coop, stat = "identity", position = "dodge", color="darkgreen")) +
#   geom_bar(aes(y=mean_playAgain, stat = "identity", position = "dodge", color="red")) +
#   ggtitle("Player ratings after each game") +
#   xlab("Game Number") +
#   theme_minimal() + 
#   theme(legend.position = "bottom")
#

@@

# First, you may need to convert the data from wide to long format
df_long <- melt(datRatings, id.vars = c("playerId", "condition", "gameNumber"),
                measure.vars = c("rating_coop", "rating_forgiving", "rating_playAgain"),
                variable.name = "rating_type", value.name = "rating_value")

>>>>

library(dplyr)
d_finished <- readRDS("../scriptMongo/data/d_finished.csv")

# Step 1: Identify the expo_opponent for each playerId where gameNumber == "11" (exposure game) & isLastRound == TRUE (to select a particular)
expo_opponent_df <- d_finished %>%
  filter(gameNumber == "11", isLastRound == TRUE) %>%
  dplyr::select(id, expo_opponent = game_opponent) %>%
  distinct() # Ensure uniqueness in case of duplicates

# Step 2: Join this information back to the original dataset
d_finished <- d_finished %>%
  left_join(expo_opponent_df, by = "id") %>%
  mutate(condition.f = as.factor(expo_opponent)) %>%
  dplyr::select(-expo_opponent) # Optionally, remove the expo_opponent column if it's no longer needed

###### get whether high or low RS and score from df_screening

# Load the "df_screening.RData" file
load("data/df_screening.RData")

RS_data <- df_screening %>% mutate(high_RS = as.factor(ifelse(RS_score > 15, 1,0))) %>% 
                            dplyr::select(id, MH.f, RS_score, high_RS)

# Find IDs for those who participated in experiment and add RS_score and high_RS as new columsn to d_finished.
# Merging d_finished with relevant columns from RS_data based on matching ids
d_finished <- d_finished %>%
  inner_join(RS_data %>% dplyr::select(id, RS_score, high_RS), by = "id")

# Summarize to count the number of participants for each Condition within each high_RS level
temp <- d_finished %>% dplyr::select(id, condition.f, high_RS) %>% 
                      unique() %>%
                      group_by(high_RS, condition.f) %>%
                      summarize(participant_count = n(), .groups = 'drop')

# View the summarized counts
print(temp)
```
```{r}
# Filter and Select Columns
result <- d_finished %>%
          filter(high_RS == 1) %>%
          dplyr::select(id, RS_score)%>% 
          unique()

# Print the Result
print(result)
```

# d_finished now has the 'Condition' column with the value equal to expo_opponent for all rounds and rows per playerId

d_finished <- d_finished  %>% mutate( gameNum.f = factor(gameNumber,labels = c("pre", "expo1", "expo2", "expo3","post"),
                                      levels=c("1", "11", "12", "13", "2"))) %>% 
                              rename(# Before Exposure
                            rating_cooperative_1 = `ratePLayer_trustGame_1.How cooperative do you think the other player is?`,
                            rating_forgiving_1 = `ratePLayer_trustGame_1.How forgiving do you think the other player is?`,
                            rating_playAgain_1 = `ratePLayer_trustGame_1.If given the choice, would you like to play again with the other player?`,

@@

                            )
```

d_finished %>% dplyr::filter(id=="601d2aa3cf8c480009fc0719")  %>% dplyr::select(Turing.justification)
```

@@

# ggplot(mu,aes(x=gameNumber)) + 
#   geom_bar(aes(y=mean_forgiv, stat = "identity", position = "dodge", color="blue")) + 
#   geom_bar(aes(y=mean_coop, stat = "identity", position = "dodge", color="darkgreen")) +
#   geom_bar(aes(y=mean_playAgain, stat = "identity", position = "dodge", color="red")) +
#   ggtitle("Player ratings after each game") +
#   xlab("Game Number") +
#   theme_minimal() + 
#   theme(legend.position = "bottom")
#   
```

@@

# First, we need to convert the data from wide to long format
df_long <- melt(datRatings, id.vars = c("playerId", "condition", "gameNumber"),
                measure.vars = c("rating_coop", "rating_forgiving", "rating_playAgain"),
                variable.name = "rating_type", value.name = "rating_value")
